---
title: "ASReview Webscrape Script"
author: "Kevin Patyk"
date: "3/28/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading the required packages
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(httr)
```

-----

# Importing the data

Loading the data which contains information about the articles that need to be downloaded as PDF files.
```{r}
df <- read.csv(file = "Article_Information.csv")
```

Double checking to make sure that the data loaded in correctly and inspecting the data.
```{r}
#getting the dimensions (rows x columns)
dim(df)
#checking the first 6 observations
head(df)
#checking the last 6 observations
tail(df)
```

Checking for the number of inclusions.
```{r}
table(df$included)
```

-----

# PDF webscrape script

It takes as input a `.csv` with a column `doi` (or just change the column name in the function `get_upwtakes`), and outputs a `.csv` with the original data and the results from unpaywall in 6 additional columns:

* `upw_doi` - the doi as it is in unpaywall
* `upw_oa` - T/F; whether upw has found an open access version
* `upw_oa_status`: gold, hybrid, bronze, green
* `upw_license`: the license of the 'best oa version' in unpaywall, if available (with publisher versions prioritized over version in a repository)
* `upw_url`: the url to the pdf or, if that's not available, to the landing page of the oa version
* `upw_url_is_pdf`: T/F; whether the url is to the pdf or not

Unpaywall takes dois in various forms (case insensitive, and with/without the url-prefixes `http://dx.doi.org` and `https://doi.org`, so the function returns the input dois as well to match back to the original dataframe, but this variable is not included in the final output.
```{r}
#setting email
email <- 'k.c.patyk@uu.nl'

#function to query Unpaywall API
#the API returns an error message in json when an invalid DOI is entered -> no need for tryCatch
get_upw <- function(doi, var_email){
  url <- paste0("https://api.unpaywall.org/v2/",
                doi,
                "?email=",
                email)
  raw_data <- httr::GET(url)
  rd <- httr::content(raw_data)
  
  res <- list(input = doi,
              output = rd)
}

#functions to add progress bar
get_upw_progress <- function(x, var_email){
  pb$tick()$print()
  res <- get_upw(x, var_email)
  
  return(res)
}


extract_upw_data <- function(x){
  
  #because upw takes dois in various forms (with or without url prefix)
  #input value is returned to enable matching back to original dataframe
  input_doi <- x$input
  
  upw_doi <- x$output %>%
    pluck("doi", .default = NA)
  
  upw_is_oa <- x$output %>%
    pluck("is_oa", .default = NA)
  
  upw_oa_status <- x$output %>%
    pluck("oa_status", .default = NA)
  
  upw_license <- x$output %>%
    pluck("best_oa_location", .default = NA) %>%
    pluck("license", .default = NA)
  
  upw_url <- x$output %>%
    pluck("best_oa_location", .default = NA) %>%
    pluck("url", .default = NA)
  
  upw_url_pdf <- x$output %>%
    pluck("best_oa_location", .default = NA) %>%
    pluck("url_for_pdf", .default = NA)
  
  res <- list(input_doi = input_doi,
              upw_doi = upw_doi,
              upw_is_oa = upw_is_oa,
              upw_oa_status = upw_oa_status,
              upw_license = upw_license,
              upw_url = upw_url,
              upw_url_pdf = upw_url_pdf)
  
  return(res)
  
}  

#----------------------------------------------

# Set email as variable "upw_email" in .Renviron
#file.edit("~/.Renviron")
# Restart R session after saving .Renviron 

# Get email for Unpaywall as variable from .Renviron
#email <- Sys.getenv("upw_email")

# import csv with dois in column doi
# if needed, rename/create column 'doi' after import, or adapt column name in function 
#set correct path and file name in next line
df <- read_csv("Article_Information.csv")

#create vector of unique dois
dois <- df %>%
  filter(!is.na(doi)) %>%
  pull(doi) %>%
  unique()


#set parameter for progress bar
#this gives a warning but still works as of 2022-03
pb <- progress_estimated(length(dois))

#get API results
res_upw <- map(dois, ~get_upw_progress(.,
                                        var_email = email))

#extract data
df_upw <- map_dfr(res_upw, extract_upw_data)

# create T/F column with indication url_is_pdf
df_upw <- df_upw %>%
  mutate(upw_url_is_pdf = case_when(
    upw_url == upw_url_pdf ~ TRUE,
    TRUE ~ FALSE)) %>%
  select(-upw_url_pdf)


#join upw columns back to original df
df_res <- df %>%
  left_join(df_upw, by = c("doi" = "input_doi"))


#write result to csv
#set path and file name in line below
write_csv(df_res, "Article_Information_res.csv")
```

----- 

# Results

Will be looking at:

* Total number of records / total number of relevant records
* No. of records with a DOI / no. of relevant records with DOI
* No. of records with a link to the full text / no. of relevant records with a link
* No. of records with full text with a permissive license / no. of relevant records with per.lic.
```{r}
#inclusions/exclusions
table(df_res$included)

#number of records with doi
sum(!is.na(df_res$doi))

#number of relevant records with doi
sum(!is.na(df_res[df_res$included == 1, ]$doi))

#number of records with link to full text
sum(!is.na(df_res$upw_url))

#number of relevant records with link
sum(!is.na(df_res[df_res$included == 1, ]$upw_url))

#number of records with full text permissive license
table(df_res$upw_license)

#number of relevant records with permissive license
table(df_res[df_res$included == 1, ]$upw_license)
```

------

# End of document

------

```{r}
sessionInfo()
```

